---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PaRe

<!-- badges: start -->
[![R-CMD-check](https://github.com/darwin-eu-dev/PaRe/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/darwin-eu-dev/PaRe/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

PaRe (**Pa**ckage **Re**viewer) is the successor of the DependencyReviewer package. PaRe reviews other packages during code review and has the following features:

1. What dependencies are used, and what functions are used of that dependency.
2. The quality of the code style using lintr.
3. Code complexity, using the *cyclomatic complexity* scores.
4. How internally defined functions interact with one another, and visualizing this in a diagram.
5. Fetching locations of defined functions in R-files.
6. Checking dependencies against user a defined white list.
7. Count lines of code for different languages by default: R, C++, SQL, and Java.
8. Make a standardized HTML-report exploring the before mentioned features.

## Installation <a name="Installation"></a>

You can install the development version of DependencyReviewer like so:
```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("darwin-eu/PaRe")
```
