---
title: "`r paste('PaRe Report:', basename(params$pkgPath))`"
author: "`r paste('PaRe', packageVersion('PaRe'))`"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
params:
  pkgPath: pkgPath
  showCode: showCode
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package overview
```{r packageDiagram, out.width="100%", echo=params$showCode, warning=FALSE}
params$pkgPath %>%
  PaRe::pkgDiagram() %>%
  DiagrammeRsvg::export_svg() %>%
  charToRaw() %>%
  magick::image_read()
```

## Summary of package functions
```{r getDefinedFunctionsPkg, echo=params$showCode, message=FALSE, warning=FALSE}
defFuns <- PaRe::getDefinedFunctionsPkg(params$pkgPath)
```

```{r summaryDefFunStats, echo=params$showCode}
DT::datatable(data.frame(
  min = c(min(defFuns$nArgs, na.rm = TRUE), 
          min(defFuns$size, na.rm = TRUE), 
          min(defFuns$cycloComp, na.rm = TRUE)),
  median = c(median(defFuns$nArgs, na.rm = TRUE), 
             median(defFuns$size, na.rm = TRUE), 
             median(defFuns$cycloComp, na.rm = TRUE)),
  max = c(max(defFuns$nArgs, na.rm = TRUE), 
          max(defFuns$size, na.rm = TRUE), 
          max(defFuns$cycloComp, na.rm = TRUE)),
  row.names = c("Number of arguments",
                "Lines of code",
                "Cyclomatic complexity")), 
  options = list(dom = 't'))
```

```{r, echo=params$showCode}
gg_nArgs <- defFuns %>% 
  ggplot2::ggplot()+
  ggplot2::geom_histogram(aes(nArgs), binwidth = 1,
                 colour = "black",
                 fill = "grey")+
  ggplot2::theme_minimal()+
  ggplot2::xlab("Number of arguments")

gg_size <- defFuns %>% 
  ggplot2::ggplot()+
  ggplot2::geom_histogram(aes(size), binwidth = 1,
                 colour = "black",
                 fill = "grey")+
  ggplot2::theme_minimal()+
  ggplot2::xlab("Lines of code")

gg_cycloComp <- defFuns %>% 
  ggplot2::ggplot()+
  ggplot2::geom_histogram(aes(cycloComp), binwidth = 1,
                 colour = "black",
                 fill = "grey")+
  ggplot2::theme_minimal()+
  ggplot2::xlab("Cyclomatic complexity")

cowplot::plot_grid(gg_nArgs, gg_size, gg_cycloComp, nrow = 3)
```

```{r, echo=params$showCode, warning=FALSE, message=FALSE}
p <- defFuns %>% 
  ggplot2::ggplot(aes(group=fun))+
  ggplot2::geom_point(aes(size, cycloComp, 
                          colour = nArgs),
                      size = 3)+
  ggplot2::scale_colour_gradient(name = "Number of\nargruments",
                               low = "blue", high = "red")  +
  ggplot2::theme_minimal() +
  ggplot2::xlab("Lines of code") +
  ggplot2::ylab("Cyclomatic complexity") +
  ggplot2::theme(legend.position = "top")

  plotly::ggplotly(p,
                  tooltip = c("group", "colour",
                              "x", "y"))
```

## Function details
```{r definedFunctions, echo=params$showCode}
colours <- c("", "#DFDF00", "#AA3F40")
argBreaks <- c(5, 7)
complexBreaks <- c(15, 30)
lineBreaks <- c(100, 200)

DT::datatable(
  defFuns %>% 
    dplyr::mutate(file_start = paste0(file, " (from line: ", start, ")")) %>% 
    dplyr::select("fun", "nArgs", "size","cycloComp", "file_start") %>% 
    dplyr::rename(
      "Function" = "fun",
      "Number of arguments" = "nArgs",
      "Lines of code" = "size",
      "Cyclomatic complexity" = "cycloComp",
      "Location" = "file_start"),
  rownames = FALSE) %>%
  DT::formatStyle("Number of arguments", backgroundColor = styleInterval(argBreaks, colours)) %>%
  DT::formatStyle("Cyclomatic complexity", backgroundColor = styleInterval(complexBreaks, colours)) %>%
  DT::formatStyle("Lines of code", backgroundColor = styleInterval(lineBreaks, colours))
```

## Use of other programming languages
```{r countLines, echo=params$showCode}
DT::datatable(
  countPackageLines(path = params$pkgPath),
  rownames = "# lines of code")
```

## Style adherence, syntax errors and possible semantic issues
### Summary
```{r lintScores, echo=params$showCode, message=FALSE, warning=FALSE}
DT::datatable(PaRe::lintScore(PaRe::lintPackage, params$pkgPath) %>% 
                dplyr::rename("Percentage of lines assessed" = "pct"),
              rownames= FALSE)
```

### Warnings
```{r lintMessages warnings, echo=params$showCode, message=FALSE, warning=FALSE}
lintMsgs <- data.frame(PaRe::lintPackage(params$pkgPath),
              rownames= FALSE)

DT::datatable(
  lintMsgs %>%
    dplyr::filter(type == "warning") %>% 
  dplyr::group_by(message) %>%
  dplyr::tally(sort = TRUE),
              rownames= FALSE
)
```

### Style
```{r lintMessages style, echo=params$showCode, message=FALSE, warning=FALSE}
DT::datatable(
  lintMsgs %>%
    dplyr::filter(type == "style") %>% 
  dplyr::group_by(message) %>%
  dplyr::tally(sort = TRUE),
              rownames= FALSE
)
```

## Dependency review
### Check dependencies against whitelist
```{r checkDependencies, echo=params$showCode, warning=FALSE}
DT::datatable(PaRe::checkDependencies(pkgPath = params$pkgPath, verbose = FALSE))
```

### Dependency characteristics
- **countVertices**: The amount of recursive dependencies `r basename(params$pkgPath)` depends on.
- **countEdges**: The total amount of imports of all dependencies.
- **meanDegree**: The average amount of imports per dependency.
- **meanDistance**: The average dependency layers between `r basename(params$pkgPath)` and all other recursive dependencies.
```{r dependencyGraphStats, echo=params$showCode, message=FALSE, warning=FALSE}
graphData <- getGraphData(path = params$pkgPath)

DT::datatable(data.frame(
  countVertices = length(igraph::V(graphData)),
  countEdges = length(igraph::E(graphData)),
  meanDegree = round(mean(igraph::degree(graphData)), 2),
  meanDistance = round(mean(igraph::distances(graphData)), 2)
  ),
              rownames= FALSE)
```

```{r farthestDependency, echo=params$showCode, message=FALSE, warning=FALSE, out.width="100%"}
p <- igraph::all_simple_paths(
  graph = graphData,
  from = basename(params$pkgPath),
  to = igraph::farthest.nodes(graphData)$vertices[2])


ggraph::ggraph(
  graph = igraph::induced_subgraph(graphData, p[[1]]),
  layout = "tree") +
  ggraph::geom_edge_link() +
  ggraph::geom_node_label(
    mapping = ggplot2::aes(
      label = name)) +
  ggplot2::theme_void()
```

### Function use per dependency
```{r summariseFunctionUse, echo=params$showCode, message=FALSE, warning=FALSE}
funsUsed <- PaRe::summariseFunctionUse(
  list.files(normalizePath(paste0(params$pkgPath, "/R")), full.names = TRUE))

DT::datatable(funsUsed,
              rownames= FALSE)
```

```{r plotFunctionUse, dpi=100, fig.height=25, out.width="100%", echo=params$showCode, message=FALSE, warning=FALSE}
function_sub <- funsUsed %>% 
  dplyr::filter(!pkg %in% c("base"))

fun_counts <- function_sub %>%
  dplyr::group_by(fun, pkg, name = "n") %>%
  dplyr::tally()

# Filter functions that are defined in the package
nonPkgFuns <- fun_counts[!fun_counts$fun %in% defFuns$fun, ]

ggplot2::ggplot(
  data = nonPkgFuns,
  mapping = ggplot2::aes(x = .data$fun, y = .data$n, fill = .data$pkg)) +
  ggplot2::geom_col() +
  ggplot2::facet_wrap(
    dplyr::vars(.data$pkg),
    scales = "free_x",
    ncol = 2) +
  ggplot2::theme_bw() +
  ggplot2::theme(
    legend.position = "none",
    axis.text.x = (ggplot2::element_text(angle = 45, hjust = 1, vjust = 1)))
```





## Further reading
### Style Guide
The styling is based on the following style guide:

- [Tidyverse styleguide](https://style.tidyverse.org/syntax.html)
- [HADES styleguide](https://ohdsi.github.io/Hades/codeStyle.html)

### Cyclomatic Complexity
>[Cyclomatic Complexity](https://en.wikipedia.org/wiki/Cyclomatic_complexity) is a software metric used to indicate the complexity of a program. It is a quantitative measure of the number of linearly independent paths through a program's source code. It was developed by Thomas J. McCabe, Sr. in 1976.

And is calculated as follows: $M = E - N + 2P$

The complexity score is interpreted as follows:

> 
> - 1-10 Simple procedure, little risk
> - 11-20 More complex, moderate risk
> - 21-50 Complex, high risk
> - \>50 Untestable code, very high risk
> 

[link, 2023-02-10](https://en.wikipedia.org/wiki/Cyclomatic_complexity#Interpretation)
